ERSPAN Support for Linux

### 2018-10-16 paper.tex
conclusion

\documentclass{sigplanconf}

@@

Metada-mode tunnel, or light weight tunnel, is designed for solving
the limitation.  The fundamental idea is that only one netdev per
tunnel type is required to represent multiple tunnels.
This means that the tunnel configuration of a particular type
of the tunnel must be passed to the tunnel netdev in order
to encapsulate the packet.  For example, creating a metadata-mode
tunnel can be done by:
\texttt{ip link add dev type gretap external}.
Note that there is no configuration parameters assigned at device creation
time. The tunnel configuration is set-up per-packet at run-time.
Currently there are two ways of using metadata-mode tunnel, one through
OVS and the other through eBPF~\cite{dborkman}.
We implement both the native mode and metadata-mode~\cite{erspanmd}
for ERSPAN type II and type III.
More examples of using native and metadata-mode tunnel are upstreamed
under tools/testing/selftest/bpf/\{test\_tunnel.sh, test\_tunnel\_kern.c\}.

@@

        return TC_ACT_OK;
}
\end{verbatim}
}
\section{Conclusion and Future Work}
\mycomment{
\section{Acknowledgments}
The authors would like to acknowledge Justin Pettit for his guidance on writing
this paper, Martynas Pumputis for providing context around WeaveNet, and Ben
Pfaff, Hannes Sowa and Yingying Ren for providing review feedback.
\section{Author Biography}
Joe Stringer is a software engineer interested in networks and related fields,
in particular SDN. He is actively engaged in the open-source community on
network software projects including Open vSwitch and the Linux networking
stack.
}
\bibliography{paper.bib}
\bibliographystyle{plain}

>>>>

\documentclass[10pt]{sigplanconf}

@@

Metada-mode tunnel, or light weight tunnel, is designed for solving
the limitation.  The fundamental idea is that only one netdev per
tunnel type is required to represent multiple tunnels.
This means that the tunnel configuration of a particular type
of the tunnel must be passed to the tunnel netdev in order
to encapsulate the packet.  For example, creating a metadata-mode
tunnel can be done by:
\texttt{ip link add dev type gretap external}.
Note that there is no configuration parameters assigned at device creation
time. The tunnel configuration is set-up per-packet at run-time.
Currently there are two ways of using metadata-mode tunnel, one through
OVS and the other through eBPF~\cite{daniel2}.
We implement both the native mode and metadata-mode~\cite{erspanmd}
for ERSPAN type II and type III.
More examples of using native and metadata-mode tunnel are upstreamed
under tools/testing/selftest/bpf/\{test\_tunnel.sh, test\_tunnel\_kern.c\}.

@@

        return TC_ACT_OK;
}
\end{verbatim}
}
\section{Conclusion}
Port mirroring is the most common troubleshooting techniques
allowing a user to send a copy of the monitored traffic to a packet analyzer.
ERSPAN extends its precedence SPAN and RSPAN, by allowing the monitored
traffic to route across IP networks.
In this paper, we describe the implementation of ERSPAN and demonstrate three
ways to use the ERSPAN protocol in Linux, by creating a native-mode ERSPAN tunnel
, or by creating eBPF byte-code with metadata-mode tunnel, or by using Open
vSwitch kernel module. 
We'd like to thank many people for giving review comments feedbacks for our
ERSPAN patches.

\mycomment{
\section{Acknowledgments}
The authors would like to acknowledge Justin Pettit for his guidance on writing
this paper, Martynas Pumputis for providing context around WeaveNet, and Ben
Pfaff, Hannes Sowa and Yingying Ren for providing review feedback.
\section{Author Biography}
Joe Stringer is a software engineer interested in networks and related fields,
in particular SDN. He is actively engaged in the open-source community on
network software projects including Open vSwitch and the Linux networking
stack.
}
\bibliography{paper.bib}
\bibliographystyle{plain}
